\Large \bf Frontrunning

### 2018-07-06 frontrunning/Latex/sections/paper.tex
[frontrunning] Restructure and notes from meeting

% !TEX root = ../main.tex
\section{Introductory Remarks}

\subsection{What is frontrunning?} %Definition of frontrunning
%Traditional
Frontrunning was first appeared on the Chicago Board Options Exchange (SBOE) ~\cite{markham1988front}, and was later defined by \textit{Secrities Exchange Comission} in 1977 as following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978cboe}
\end{quote} 
On the years after there were ongoing discussions between self-regulatory exchanges and SEC to regulate, detect and define laws to deal with frontrunning~\cite{markham1988front}, with SEC stating: 
\begin{quote}
it seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBOE).}
\end{quote} 
% http://3197d6d14b5f19f2f440-5e13d29c4c016cf96cbbfd197c579b45.r81.cf1.rackcdn.com/collection/papers/1970/1978_OptMkt_06_Chapter_III_3.pdf
Initially the frontrunning policies only applied to certain options, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{sec2012frontrunning}.

@@

\textbf{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc. In the blockchain world, everyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain. Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however the decentral application could be designed in such a way to prevent frontrunning attacks.

%WRT blockchain and decentralization
\subsection{Miners and their power}
%Transaction order, can be used for frontrunning

@@

\section{Related Work}

@@

\section{Comparison Framework}

Solutions: \par\noindent
Criteria:

@@

@@

@@

@@

Commit / reveal methods %namecoin story @mahsa
\begin{itemize}
\item{Send the hash first, send the actual data after (sealed-bid auctions)}
\item{Proof of burn methods (generate random addresses with no private keys)}
\end{itemize}
Submarines
\begin{itemize}
\item{The method described in HD can be optimized and more functional with the new changes to ethereum and solidity}
\item{Submarines 2.0: There can be a new way of doing this (new WRT hackingditributed article), can predict smart contract addresses using the nonce and data of the contract (forwarder/refunder), so funds can be sent to these addresses and then contracts can be deployed}
\begin {itemize}
\item{Pros: new addresses, no indication of the order (Anonymity-set)}
\item{Cons: DDoS? Requires 3 transactions for each order?} >> 1 send the funds 2 Deploy the contract 3 call the function
\end{itemize}
\item{Other methods? Consensus protocol based solutions?}

\end{itemize}
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

@@

>>>>

% !TEX root = ../main.tex

\section{Introduction}

% PAPER BEING SOLD HERE

\section{Priliminary}

\subsection{What is frontrunning?} %Definition of frontrunning

%Traditional

%talking about front running

%Miners in Bitcoin can do selfish mining and such but in theory
% here we talk about miners actually being malicious(?) to profit themselves.

@@

% ticket scalping : https://en.wikipedia.org/wiki/Ticket_resale

\subsection{Historical Context}
Frontrunning was first appeared on the Chicago Board Options Exchange (SBOE) ~\cite{markham1988front}, and was later defined by \textit{Secrities Exchange Comission} in 1977 as following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978cboe}
\end{quote} 
On the years after there were ongoing discussions between self-regulatory exchanges and SEC to regulate, detect and define laws to deal with frontrunning~\cite{markham1988front}, with SEC stating: 
\begin{quote}
it seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBOE).}
\end{quote} 
% http://3197d6d14b5f19f2f440-5e13d29c4c016cf96cbbfd197c579b45.r81.cf1.rackcdn.com/collection/papers/1970/1978_OptMkt_06_Chapter_III_3.pdf
Initially the frontrunning policies only applied to certain options, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{sec2012frontrunning}.

\subsection{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc. In the blockchain world, everyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain. Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however the decentral application could be designed in such a way to prevent frontrunning attacks.

\subsection{Related Work}

% Shayan: talk about frontrunning in other blockchains, such as privacy preserving blockchains --> no transparency less chance of frontrunning?  
% this is a big problem with Dapps, what other blockchains support smart contracts that have this problem.

% Mahsa: talk about namecoin frontrunning from the paper

% NOTE: use double-spend paper (first)
% talk about double-spend one kind of frontrunning (relationship between frontrunning vs double spend) rushing actors. 
% Double-spending fast payments in bitcoin.pdf

@@

@@

%\section{Comparison Framework}

@@

%NOTE: top 10 dapps, talk about frontrunning attacks on them.

@@

\section{Potential Front runners} % Who and How.

%WRT blockchain and decentralization

% TALK ABOUT IT {Miners and their power}

%Transaction order, can be used for frontrunning

\subsection{Miners}

% Mining blocks hence order of the transactions within a block --> reorder
%

% Use example of the paper, talk about status ICO or some other miner reorder frontrunning

\subsection{non-miner}
% Use high gasprice to get infront
% Sybil attacks?
%

% Use example of  namecoin/domain . use an example of Alice wants to register a domain and bob uses GasPrice to get in front of Alice.

@@

% ICOs and ceiling
% hard cap --> frontrun and buy the tokens in big chunk
% dynamic ceiling, fair token distribution --> status ICO

@@

Commit / reveal methods %namecoin story @mahsa 
% 1) Go dark
\begin{itemize}
\item{Send the hash first, send the actual data after (sealed-bid auctions)}
\item{Proof of burn methods (generate random addresses with no private keys)}
\end{itemize}
Submarines
\begin{itemize}
\item{The method described in HD can be optimized and more functional with the new changes to ethereum and solidity}
\item{Submarines 2.0: There can be a new way of doing this (new WRT hackingditributed article), can predict smart contract addresses using the nonce and data of the contract (forwarder/refunder), so funds can be sent to these addresses and then contracts can be deployed}
\begin {itemize}
\item{Pros: new addresses, no indication of the order (Anonymity-set)}
\item{Cons: DDoS? Requires 3 transactions for each order?} >> 1 send the funds 2 Deploy the contract 3 call the function
\end{itemize}
\item{Other methods? Consensus protocol based solutions?}

% How are we solving this in orderbooks?
%shayan: Give the fees in a decental orderbook to the miners so change the incentive model and they are incentivized to act honestly
%2) kill the incentive (change the incentive) ^ .

% also call options on a random ending block, so timing of the incoming transactiion does not matter

%3) change the mechanics. similar to double spend mitigation, fee structure. with gas limits gasprice limit (status ico did. and bancor after the attack)

@@

% @shayan:
% Could talk about a tool / a framework to detect frontrunning
% Circle in the py-etherscan guy about having the tools to detect such things
